Supplement to Automatic Matching of Bullet Lands

### 2016-04-20 revision/response.Rmd

34. p. 18, l. -4:  Change "this study" to "that study", so the reader is certain you mean Ma et al. (2001) and not your own.

***DONE***

35. p. 20,  l. -3:  I really like the idea of including an inconclusive zone.

***Thank you for the comment. We have chosen to leave off a more detailed discussion on an inconclusive zone. Certainly, formulating such a zone would have important implications in terms of the criminal justice system, but it is one that we felt was outside the scope of this particular paper. Certainly, should an automated algorithm like we propose be used as an aid in the conviction or the exoneration of suspects, much attention would be needed on the extent of this zone.***

### 2016-04-20 imaging-paper.Rnw
More comments

Besides resulting in a probabilistic quantification of matches, random forests also provide an assessment of the importance of each of the features derived from the bullets' 3D topological surface measurements. Figure~\ref{fig:importance} shows an overview of the importance of each variable measured as the mean decrease in the Gini index when the variable in question is included in a tree (for the exact values please refer to Supplement section~\ref{supp:randomforest}). 
\begin{figure}
<<echo=FALSE, fig.width=7, fig.height=2, out.width='.7\\textwidth'>>=
imp <- data.frame(importance(rtrees))
imp$Variable <- row.names(imp)
imp$Variable[c(7,8)] <- c("#matches", "#non-matches")
imp1 <- subset(imp, !(Variable %in% c("x1", "sd.D", "S")))
imp2 <- subset(imp, Variable %in% c("x1", "sd.D", "S"))
qplot(MeanDecreaseGini,1, data=imp, geom="point") + 
  geom_text(aes(y=1.2, label=Variable), angle=45, hjust=0, data=imp1) + 
  geom_text(aes(y=0.8, label=Variable), angle=-45, hjust=0, data=imp2) + 
  ylim(c(0, 2.75)) + theme_bw() + ylab("") +
  theme(axis.ticks.y=element_blank(), axis.text.y=element_blank(),
        panel.grid.major.y=element_blank(), panel.grid.minor.y=element_blank()) +
  xlab("Importance (mean decrease in Gini index)")
@
\caption{\label{fig:importance}Importance of features in the random forest. Importance is measured in terms of mean decrease in gini index when including the variable in a decision tree.}
\end{figure}

>>>>

Besides resulting in a probabilistic quantification of matches, random forests also provide an assessment of the importance of each of the features derived from the bullets' 3D topological surface measurements. Figure~\ref{fig:importance} shows an overview of the importance of each variable measured as the mean decrease in the Gini index when the variable in question is included in a tree (for the exact values please refer to Supplement section~\ref{supp:randomforest}). 
\begin{figure}
<<echo=FALSE, fig.width=7, fig.height=2, out.width='.7\\textwidth'>>=
imp <- data.frame(importance(rtrees))
imp$Variable <- row.names(imp)
imp$Variable[c(7,8)] <- c("#matches", "#non-matches")
imp1 <- subset(imp, !(Variable %in% c("x1", "sd.D", "S")))
imp2 <- subset(imp, Variable %in% c("x1", "sd.D", "S"))
imp3 <- subset(imp, !(Variable %in% c("x1", "x2", "sd.D", "lag")))
qplot(MeanDecreaseGini,1, data=imp3, geom="point") + 
  geom_text(aes(y=1.2, label=Variable), angle=45, hjust=0, data=subset(imp3, Variable != "S")) + 
  geom_text(aes(y=1.2, label=Variable), angle=45, vjust=1.2, hjust=0, data=subset(imp3, Variable == "S")) + 
  ylim(c(0, 2.75)) + theme_bw() + ylab("") +
  theme(axis.ticks.y=element_blank(), axis.text.y=element_blank(),
        panel.grid.major.y=element_blank(), panel.grid.minor.y=element_blank()) +
  xlab("Importance (mean decrease in Gini index)")
@
\caption{\label{fig:importance}Importance of features in the random forest. Importance is measured in terms of mean decrease in gini index when including the variable in a decision tree.}
\end{figure}

### 2016-04-20 imaging-supplement.Rnw
More comments

imp$meanMatch <- round(imp$meanMatch,1)
imp$sdMatch <- sprintf("(%5.2f)", imp$sdMatch)
imp$meanNonMatch <- round(imp$meanNonMatch,1)
imp$sdNonMatch <- sprintf("(%7.2f)", imp$sdNonMatch)
row.names(imp) <- 1:nrow(imp)
imp$Variable[c(2,3,4,6,8)] <- c("#matches", "S", "#non-matches", "CMS", "CNMS")
names(imp)[-(1:3)] <- c("KM", "(sd)", "KNM", "(sd)")
print(xtable(imp, align="clrrrd{3.2}rd{3.2}", digits=c(0,0,1,1,1,2,1,2)), 
      floating = FALSE)
@
\end{table}

>>>>

imp$meanMatch <- round(imp$meanMatch,1)
imp$sdMatch <- sprintf("(%5.2f)", imp$sdMatch)
imp$meanNonMatch <- round(imp$meanNonMatch,1)
imp$sdNonMatch <- sprintf("(%7.2f)", imp$sdNonMatch)
row.names(imp) <- 1:nrow(imp)
imp$Variable[c(2,3,4,6,8)] <- c("#matches", "S", "#non-matches", "CMS", "CNMS")
names(imp)[-(1:3)] <- c("KM", "(sd)", "KNM", "(sd)")

result <- subset(imp, !(Variable %in% c("x1", "x2", "lag", "sd.D")))
rownames(result) <- 1:nrow(result)

print(xtable(result, align="clrrrd{3.2}rd{3.2}", digits=c(0,0,1,1,1,2,1,2)), 
      floating = FALSE)
@
\end{table}

### 2016-04-20 imaging-supplement.tex
More comments

\begin{table}[tbhp]
\caption{\label{tab:importance}Table of  features derived from bullet image ordered by importance in predicting matches. Importance is measured in terms of mean decrease in gini index when including the variable in a decision tree. Averages (and standard deviations) for known matches (KM) and known non-matches (KNM) are shown in the last four columns.}
\centering
% latex table generated in R 3.2.4 by xtable 1.8-2 package
% Tue Apr  5 08:28:49 2016
\begin{tabular}{clrrrd{3.2}rd{3.2}}
  \hline
 & Variable & Importance 1 & Importance 2 & KM & (sd) & KNM & (sd) \\ 
  \hline
1 & ccf & 87.0 & 134.6 & 0.7 & ( 0.25) & 0.3 & (   0.10) \\ 
  2 & \#matches & 81.9 & 128.3 & 15.5 & ( 7.91) & 4.3 & (   2.51) \\ 
  3 & S & 46.4 & 53.6 & 18.3 & ( 8.95) & 5.5 & (   3.41) \\ 
  4 & \#non-matches & 35.9 & 62.7 & 9.8 & ( 5.80) & 18.8 & (   3.92) \\ 
  5 & D & 26.1 & 45.7 & 1.9 & ( 2.32) & 3.3 & (   1.94) \\ 
  6 & CMS & 15.9 & 25.1 & 8.5 & ( 5.65) & 2.3 & (   1.40) \\ 
  7 & sd.D & 15.0 & 23.6 & 2.9 & ( 0.80) & 2.9 & (   0.70) \\ 
  8 & CNMS & 13.3 & 20.9 & 4.8 & ( 4.10) & 10.2 & (   4.35) \\ 
  9 & lag & 9.9 & 17.0 & 200.8 & (48.29) & 204.0 & ( 113.63) \\ 
  10 & x2 & 4.2 & 6.2 & 166.5 & (81.07) & 163.5 & (  72.30) \\ 
  11 & x1 & 3.9 & 6.1 & 175.0 & (71.59) & 175.0 & (  71.40) \\ 
   \hline
\end{tabular}

>>>>

\begin{table}[tbhp]
\caption{\label{tab:importance}Table of  features derived from bullet image ordered by importance in predicting matches. Importance is measured in terms of mean decrease in gini index when including the variable in a decision tree. Averages (and standard deviations) for known matches (KM) and known non-matches (KNM) are shown in the last four columns.}
\centering
% latex table generated in R 3.2.4 by xtable 1.8-2 package
% Wed Apr 20 10:17:06 2016
\begin{tabular}{clrrrd{3.2}rd{3.2}}
  \hline
 & Variable & Importance 1 & Importance 2 & KM & (sd) & KNM & (sd).1 \\ 
  \hline
1 & ccf & 87.0 & 134.6 & 0.7 & ( 0.25) & 0.3 & (   0.10) \\ 
  2 & \#matches & 81.9 & 128.3 & 15.5 & ( 7.91) & 4.3 & (   2.51) \\ 
  3 & S & 46.4 & 53.6 & 18.3 & ( 8.95) & 5.5 & (   3.41) \\ 
  4 & \#non-matches & 35.9 & 62.7 & 9.8 & ( 5.80) & 18.8 & (   3.92) \\ 
  5 & D & 26.1 & 45.7 & 1.9 & ( 2.32) & 3.3 & (   1.94) \\ 
  6 & CMS & 15.9 & 25.1 & 8.5 & ( 5.65) & 2.3 & (   1.40) \\ 
  7 & CNMS & 13.3 & 20.9 & 4.8 & ( 4.10) & 10.2 & (   4.35) \\ 
   \hline
\end{tabular}
